Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-08 manuscript/draft_rsfmri.Rmd
changed directory to txt files

```{r Load data, include=FALSE}
source("code/get_subject_ID_group_tp_forSwE.R")
final = txt_for_swe(group = "all", tp = "all")

@@

```{r baseline characteristics, include=FALSE}
dfBL <- txt_for_swe(group = "all", tp = "BL")

>>>>

```{r Load data, include=FALSE}
source("code/create_sample_df.R")
final = create_sample_df(group = "all", tp = "all")

@@

```{r baseline characteristics, include=FALSE}
dfBL <- create_sample_df(group = "all", tp = "BL")
